Language and vision in conceptual processing: Multilevel analysis and statistical power

### 2022-10-29 manuscript/manuscript.Rmd
29102022

library(papaja)       # APA-formatted manuscript
library(knitr)        # Document rendering
options(kableExtra.latex.load_packages = FALSE,   # instead, LaTeX packages loaded in header/preamble above
        knitr.graphics.rel_path = FALSE)          # avoid warning (https://github.com/yihui/knitr/issues/2119#issuecomment-1092411877)
knitr::opts_knit$set(root.dir = '../')            # move working directory to the project root
library(kableExtra)   # Tables
library(dplyr)        # Data wrangling
library(formattable)  # Format numbers
library(kableExtra)   # Table formatting (e.g., `pack_rows()`)
library(stringr)      # Text processing
library(car)          # Analysis
library(lmerTest)     # Analysis
library(simr)         # Analysis
library(ggplot2)      # Plots
library(ggridges)     # Plots
library(ggtext)       # Plots
library(GGally)       # Correlation plots
library(sjPlot)       # Model plots
library(RColorBrewer) # Colours in plots
library(patchwork)    # Combination of plots
library(Cairo)        # Allows use of special characters such as dashes in plots
library(magick)       # Image rendering
library(tikzDevice)   # Image rendering

>>>>

library(papaja)       # APA-formatted manuscript
library(knitr)        # Document rendering
options(kableExtra.latex.load_packages = FALSE,   # instead, LaTeX packages loaded in header/preamble above
        knitr.graphics.rel_path = FALSE)          # avoid warning (https://github.com/yihui/knitr/issues/2119#issuecomment-1092411877)
knitr::opts_knit$set(root.dir = '../')            # move working directory to the project root
library(kableExtra)   # Tables
library(dplyr)        # Data wrangling
library(reshape2)     # Data wrangling
library(formattable)  # Format numbers
library(kableExtra)   # Table formatting (e.g., `pack_rows()`)
library(stringr)      # Text processing
library(car)          # Analysis
library(lmerTest)     # Analysis
library(simr)         # Analysis
library(ggplot2)      # Plots
library(ggridges)     # Plots
library(ggtext)       # Plots
library(GGally)       # Correlation plots
library(sjPlot)       # Model plots
library(RColorBrewer) # Colours in plots
library(patchwork)    # Combination of plots
library(Cairo)        # Allows use of special characters such as dashes in plots
library(magick)       # Image rendering
library(tikzDevice)   # Image rendering
